Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-01-30 numerical-amr.tex
interim update on refinement stuff.
updating refinement criteria section (3.1.x).

\item{\em Baryon mass.}  This refinement criteria is identified to mimic a Lagrangian method in that it tries to keep a fixed mass resolution.  In this method, a cell is refined if the baryonic mass in the cell ($M_g = \rho \Delta_x^d$) is larger than a specified value:
\begin{equation}
M_g > \rho_{\rm flag} {\Delta x^d_{\rm root}} r^{\epsilon_l l},
\end{equation}
where $\rho_{\rm flag}$ is the equivalent density on the root grid required for refinement, $\Delta x_{\rm root}$ is the root grid cell spacing, $r$ is the refinement factor, $l$ is the level and $\epsilon_l$ is a parameter which can be used to make the refinement faster ($\epsilon_l < 0$) or slower than pure Lagrangian refinement ($\epsilon_l > 0$).

@@

\item{\em Particle (dark matter) mass.}  This refinement criteria is precisely the same as the baryon overdensity criteria except it uses the grided (CIC) particle density.

\item{\em Jeans Length.}  Following \cite{Truelove98}, the code can be forced to refine the Jeans length by a fixed number of cells, or, in more specifically, whenever the following criteria is not met:
\begin{equation}
\Delta x < \left( \frac{\pi k_B T}{J^2 G \rho m_H} \right)^{1/2}
\end{equation}
where $J$ is the required number of cells per Jeans length (4 by default).

@@

>>>>

\item{\em Baryon mass.}  This refinement criterion is identified to mimic a Lagrangian method in that it tries to keep a fixed mass resolution.  In this method, a cell is refined if the baryonic mass in the cell ($M_g = \rho \Delta_x^d$) is larger than a specified value:
\begin{equation}
M_g > \rho_{\rm flag} {\Delta x^d_{\rm root}} r^{\epsilon_l l},
\end{equation}
where $\rho_{\rm flag}$ is the equivalent density on the root grid required for refinement, $\Delta x_{\rm root}$ is the root grid cell spacing, $r$ is the refinement factor, $l$ is the level and $\epsilon_l$ is a parameter which can be used to make the refinement faster ($\epsilon_l < 0$) or slower than pure Lagrangian refinement ($\epsilon_l > 0$).

@@

\item{\em Particle (dark matter) mass.}  This refinement criterion is precisely the same as the baryon overdensity criterion except it uses the grided (CIC) particle density.

\item{\em Jeans Length.}  Following \cite{Truelove98}, the code can be forced to refine the Jeans length by a fixed number of cells, or, in more specifically, whenever the following criterion is not met:
\begin{equation}
\Delta x < \left( \frac{\pi k_B T}{J^2 G \rho m_H} \right)^{1/2}
\end{equation}
where $J$ is the required number of cells per Jeans length (4 by default).

@@

\item{\em Optical depth.} This refinement criterion ensures that cells on the highest level of refinement have an HI optical depth lower than unity.  The optical depth of a cell is estimated to be:

\begin{equation}
\tau = \sigma_{HI} n_{HI} \Delta x 
\end{equation}

where $\sigma_{HI}$ is the neutral atomic hydrogen absorption cross section, $n_{HI}$ is the proper HI number density, and $\Delta x$ is the cell width.  If $\tau > 1$, the cell is refined further, up to the maximum level of refinement.

\item{\em Resistive length.}  In a way similar to the Jeans length criterion described above, the code can be forced to locally resolve the resistive length scale by a minimum of a fixed number of cells.  This is done by ensuring that the resistive length scale, defined as

\begin{equation}
L_R = |B| / |\nabla \times B|
\end{equation}

is always refined by at least N cells locally (i.e., refine a given cell further if $L_R \leq N \Delta x$).

\item{\em ``Must refine region''}.  This refinement criterion is used to ensure that all cells in a given subvolume of the simulation are refined to {\it at least} some minimum level of refinement.  The subvolume is user-specified, and may evolve over time (e.g., to follow a structure of interest that is traveling through the simulation volume).

\item{\em Metallicity.}  This refinement criterion ensures that all cells with a metallicity (defined as $Z = \equiv \rho_{Z} / \rho_{b} / 0.022$, where $\rho_{Z}$ is the density of metals in the cell, $\rho_{b}$ is the total baryon density (including metals), and 0.022 is the solar metal fraction) above a user-defined value is refined to {\it at least} some minimum level of refinement.
